MSE and dynamic state variable model with sigma function

### 2017-08-16 doc/MSE.tex
added fisures to the text

\documentclass[12pt,oneline,a4paper,numbib]{ouparticle}

\begin{document}

@@

@@

\item
Scenario I,  decrease the quota on both species to reach the Fmsy.
Reduce the IQs in the same percentage as the change in HR to reach the equilibrium (MSY).

\item 
Scenario II, decrease the quota on sp 1 and unconstrained quota for species 2.
CONSTRAINED fishery for sp1 and UNCONSTRAINED sp2 (FIXING QUOTA SP2 to 200). Only sp1 is forced to try to reach the Fmsy. However discarding is allowed for both species.

\item
Scenario III, same as scenario II but allowing to discard only species 2.

\item
Scenario IV, Same as scenario I but allowing to discard sp2.
\end{enumerate}

@@

>>>>

\documentclass[12pt,oneline,a4paper,numbib]{ouparticle}
\usepackage{array,multirow,graphicx}
\begin{document}

@@

\begin{table}[!h]
\centering
\caption{}
\label{scenarios}
\begin{tabular}{|c |c | c |}
\hline
 \parbox[c]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{\textbf{Naive manager}}}} 
 & &  \\
 & Discarding allowed & \\
 & Manager only perceives $L$ &\\
 & assuming that $C = L$  &\\
 & YPR based in $F_L$  & \\
 & assuming $L/C=1$    & No discarding allowed\\
 & & $C = L$ \\\cline{1-2}
  \parbox[c]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{\textbf{Smart manager}}}} 
 & &  Advice and quota\\
 & Discarding allowed & based on $C = L$\\
 & Manager perceives $L$ and $D$ & \\
 & assuming that $C = L + D$ &\\
 & YPR based in $F_C$  &\\
 & assuming $L/C \neq 1$ &\\
  & &  \\\hline

 & \textbf{NO LO}              & \textbf     {LO}                                  \\ \hline
\end{tabular}
\end{table}

@@

\item
Scenario I: \textbf{NO LO + Naive manager},  decrease the quota on both species to reach the Fmsy.
Reduce the IQs in the same percentage as the change in HR to reach the equilibrium (MSY).

\item 
Scenario II: \textbf{NO LO + Smart manager}, decrease the quota on sp 1 and unconstrained quota for species 2.
CONSTRAINED fishery for sp1 and UNCONSTRAINED sp2 (FIXING QUOTA SP2 to 200). Only sp1 is forced to try to reach the Fmsy. However discarding is allowed for both species.

\item
Scenario III: \textbf{LO}, same as scenario II but allowing to discard only species 2.

%\item
%Scenario IV, Same as scenario I but allowing to discard sp2.
\end{enumerate}

@@

Scenario III:
%----------------------------------------------------------------------------------------------------------------------------------------

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catch_LO.eps} 
\caption{}
\label{fig:catch_lo}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Effort_LO.eps} 
\caption{}
\label{fig:effort_lo}
\end{figure}
%----------------------------------------------------------------------------------------------------------------------------------------
